### 2020-04-27 Temp_tables/Temp_tables_revision/03_Paper_version_Revised/09_decile_6.tex
back up before new paper

\begin{document}% Date and time: Sat, Apr 04, 2020 - 09:19:22
\begin{table}[!htbp] \centering 
  \caption{Baseline regression} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{Dependent variable: \text { SO2 emission }_{i k t}} \\ 
\cline{2-7} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\
 \\[-1.8ex]& Output & Capital & Labour & Output & Capital & Labour\\
 \hline \\[-1.8ex] 
  output_{cit} & 0.136 & 0.136 & 0.137 & $-$0.059 & $-$0.059 & $-$0.059 \\ 
  & (0.154) & (0.154) & (0.154) & (0.114) & (0.114) & (0.113) \\ 
  capital_{cit} & 1.511$^{**}$ & 1.513$^{**}$ & 1.511$^{**}$ & 0.929$^{*}$ & 0.933$^{**}$ & 0.937$^{**}$ \\ 
  & (0.733) & (0.735) & (0.735) & (0.476) & (0.475) & (0.474) \\ 
  labour_{cit} & 3.038$^{***}$ & 3.041$^{***}$ & 3.035$^{***}$ & 1.550 & 1.545 & 1.538 \\ 
  & (0.829) & (0.831) & (0.829) & (1.023) & (1.023) & (1.021) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.304$^{**}$ & $-$0.305$^{**}$ & $-$0.324$^{**}$ & $-$0.298$^{**}$ & $-$0.336$^{**}$ & $-$0.377$^{**}$ \\ 
  & (0.124) & (0.135) & (0.136) & (0.142) & (0.154) & (0.154) \\ 
   TCZ_c \times \text{Period} \times \text{output share SOE}_{i}  & $-$0.187 &  &  & $-$0.824 &  &  \\ 
  & (0.390) &  &  & (0.515) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{output share SOE}_{i}  & 1.127$^{**}$ &  &  & 1.315$^{**}$ &  &  \\ 
  & (0.533) &  &  & (0.609) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{capital share SOE}_{i}  &  & $-$0.082 &  &  & $-$0.682$^{*}$ &  \\ 
  &  & (0.311) &  &  & (0.399) &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{capital share SOE}_{i}  &  & 0.744$^{*}$ &  &  & 1.065$^{**}$ &  \\ 
  &  & (0.431) &  &  & (0.513) &  \\ 
   TCZ_c \times \text{Period} \times \text{labour share SOE}_{i}  &  &  & $-$0.112 &  &  & $-$1.020$^{**}$ \\ 
  &  &  & (0.410) &  &  & (0.518) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{labour share SOE}_{i}  &  &  & 0.958$^{*}$ &  &  & 1.532$^{**}$ \\ 
  &  &  & (0.528) &  &  & (0.598) \\ 
 \hline \\[-1.8ex] 
City fixed effects & Yes & Yes & Yes & No & No & No \\ 
Industry fixed effects & Yes & Yes & Yes & No & No & No \\ 
Year fixed effects & Yes & Yes & Yes & No & No & No \\ 
City-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
Industry-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
City-industry fixed effects & No & No & No & Yes & Yes & Yes \\ 
Observations & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 \\ 
R$^{2}$ & 0.346 & 0.346 & 0.346 & 0.851 & 0.851 & 0.851 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
Due to limited space, only the coefficients of interest are presented for the regressions with city,industry, year fixed effect (i.e. columns 1-3).
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\% \
heteroscedasticity-robust standard errors in parentheses are clustered by city 
}

>>>>

\begin{document}% Date and time \times Sat, Apr 04, 2020 - 14:45:34
\begin{table}[!htbp] \centering 
  \caption{Decile 6} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{Dependent variable \times \text { SO2 emission }_{i k t}} \\ 
\cline{2-7} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\
 \\[-1.8ex]& Output & Capital & Labour & Output & Capital & Labour\\
 \hline \\[-1.8ex] 
  output_{cit} & 0.136 & 0.136 & 0.137 & $-$0.060 & $-$0.060 & $-$0.060 \\ 
  & (0.155) & (0.155) & (0.155) & (0.114) & (0.114) & (0.113) \\ 
  capital_{cit} & 1.513$^{**}$ & 1.513$^{**}$ & 1.512$^{**}$ & 0.924$^{*}$ & 0.928$^{**}$ & 0.932$^{**}$ \\ 
  & (0.735) & (0.737) & (0.737) & (0.474) & (0.473) & (0.472) \\ 
  labour_{cit} & 3.050$^{***}$ & 3.055$^{***}$ & 3.044$^{***}$ & 1.587 & 1.586 & 1.584 \\ 
  & (0.827) & (0.829) & (0.828) & (0.998) & (0.996) & (0.992) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 6}_{i} & $-$0.358$^{***}$ & $-$0.373$^{***}$ & $-$0.393$^{***}$ & $-$0.320$^{**}$ & $-$0.364$^{**}$ & $-$0.406$^{***}$ \\ 
  & (0.123) & (0.134) & (0.135) & (0.142) & (0.152) & (0.153) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 6}_{i} \times \text{output share SOE}_{i}  & 1.373$^{**}$ &  &  & 1.245$^{*}$ &  &  \\ 
  & (0.536) &  &  & (0.694) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 6}_{i} \times \text{capital share SOE}_{i}  &  & 0.962$^{**}$ &  &  & 1.046$^{**}$ &  \\ 
  &  & (0.426) &  &  & (0.531) &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 6}_{i} \times \text{labour share SOE}_{i}  &  &  & 1.240$^{**}$ &  &  & 1.520$^{**}$ \\ 
  &  &  & (0.537) &  &  & (0.654) \\ 
 \hline \\[-1.8ex] 
City fixed effects & Yes & Yes & Yes & No & No & No \\ 
Industry fixed effects & Yes & Yes & Yes & No & No & No \\ 
Year fixed effects & Yes & Yes & Yes & No & No & No \\ 
City-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
Industry-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
City-industry fixed effects & No & No & No & Yes & Yes & Yes \\ 
Observations & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 \\ 
R$^{2}$ & 0.346 & 0.346 & 0.346 & 0.851 & 0.851 & 0.851 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
Due to limited space, only the coefficients of interest are presented 
for the regressions with city,industry, year fixed effect (i.e. columns 1-3).
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\% \
heteroscedasticity-robust standard errors in parentheses are clustered by city 
}

### 2020-04-27 Temp_tables/Temp_tables_revision/03_Paper_version_Revised/10_decile_7.tex
back up before new paper

\begin{document}% Date and time \times Sat, Apr 04, 2020 - 14:45:34
\begin{table}[!htbp] \centering 
  \caption{Decile 6} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{Dependent variable \times \text { SO2 emission }_{i k t}} \\ 
\cline{2-7} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\
 \\[-1.8ex]& Output & Capital & Labour & Output & Capital & Labour\\
 \hline \\[-1.8ex] 
  output_{cit} & 0.136 & 0.136 & 0.137 & $-$0.060 & $-$0.060 & $-$0.060 \\ 
  & (0.155) & (0.155) & (0.155) & (0.114) & (0.114) & (0.113) \\ 
  capital_{cit} & 1.513$^{**}$ & 1.513$^{**}$ & 1.512$^{**}$ & 0.924$^{*}$ & 0.928$^{**}$ & 0.932$^{**}$ \\ 
  & (0.735) & (0.737) & (0.737) & (0.474) & (0.473) & (0.472) \\ 
  labour_{cit} & 3.050$^{***}$ & 3.055$^{***}$ & 3.044$^{***}$ & 1.587 & 1.586 & 1.584 \\ 
  & (0.827) & (0.829) & (0.828) & (0.998) & (0.996) & (0.992) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 6}_{i} & $-$0.358$^{***}$ & $-$0.373$^{***}$ & $-$0.393$^{***}$ & $-$0.320$^{**}$ & $-$0.364$^{**}$ & $-$0.406$^{***}$ \\ 
  & (0.123) & (0.134) & (0.135) & (0.142) & (0.152) & (0.153) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 6}_{i} \times \text{output share SOE}_{i}  & 1.373$^{**}$ &  &  & 1.245$^{*}$ &  &  \\ 
  & (0.536) &  &  & (0.694) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 6}_{i} \times \text{capital share SOE}_{i}  &  & 0.962$^{**}$ &  &  & 1.046$^{**}$ &  \\ 
  &  & (0.426) &  &  & (0.531) &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 6}_{i} \times \text{labour share SOE}_{i}  &  &  & 1.240$^{**}$ &  &  & 1.520$^{**}$ \\ 
  &  &  & (0.537) &  &  & (0.654) \\ 
 \hline \\[-1.8ex] 
City fixed effects & Yes & Yes & Yes & No & No & No \\ 
Industry fixed effects & Yes & Yes & Yes & No & No & No \\ 
Year fixed effects & Yes & Yes & Yes & No & No & No \\ 
City-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
Industry-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
City-industry fixed effects & No & No & No & Yes & Yes & Yes \\ 
Observations & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 \\ 
R$^{2}$ & 0.346 & 0.346 & 0.346 & 0.851 & 0.851 & 0.851 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
Due to limited space, only the coefficients of interest are presented 
for the regressions with city,industry, year fixed effect (i.e. columns 1-3).
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\% \
heteroscedasticity-robust standard errors in parentheses are clustered by city 
}

>>>>

\begin{document}% Date and time \times Sat, Apr 04, 2020 - 14:51:25
\begin{table}[!htbp] \centering 
  \caption{Decile 7} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{Dependent variable \times \text { SO2 emission }_{i k t}} \\ 
\cline{2-7} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\
 \\[-1.8ex]& Output & Capital & Labour & Output & Capital & Labour\\
 \hline \\[-1.8ex] 
  output_{cit} & 0.136 & 0.136 & 0.137 & $-$0.059 & $-$0.059 & $-$0.059 \\ 
  & (0.154) & (0.154) & (0.154) & (0.114) & (0.114) & (0.113) \\ 
  capital_{cit} & 1.511$^{**}$ & 1.513$^{**}$ & 1.511$^{**}$ & 0.929$^{*}$ & 0.933$^{**}$ & 0.937$^{**}$ \\ 
  & (0.733) & (0.735) & (0.735) & (0.476) & (0.475) & (0.474) \\ 
  labour_{cit} & 3.038$^{***}$ & 3.041$^{***}$ & 3.035$^{***}$ & 1.550 & 1.545 & 1.538 \\ 
  & (0.829) & (0.831) & (0.829) & (1.023) & (1.023) & (1.021) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 7}_{i} & $-$0.304$^{**}$ & $-$0.305$^{**}$ & $-$0.324$^{**}$ & $-$0.298$^{**}$ & $-$0.336$^{**}$ & $-$0.377$^{**}$ \\ 
  & (0.124) & (0.135) & (0.136) & (0.142) & (0.154) & (0.154) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 7}_{i} \times \text{output share SOE}_{i}  & 1.127$^{**}$ &  &  & 1.315$^{**}$ &  &  \\ 
  & (0.533) &  &  & (0.609) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 7}_{i} \times \text{capital share SOE}_{i}  &  & 0.744$^{*}$ &  &  & 1.065$^{**}$ &  \\ 
  &  & (0.431) &  &  & (0.513) &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 7}_{i} \times \text{labour share SOE}_{i}  &  &  & 0.958$^{*}$ &  &  & 1.532$^{**}$ \\ 
  &  &  & (0.528) &  &  & (0.598) \\ 
 \hline \\[-1.8ex] 
City fixed effects & Yes & Yes & Yes & No & No & No \\ 
Industry fixed effects & Yes & Yes & Yes & No & No & No \\ 
Year fixed effects & Yes & Yes & Yes & No & No & No \\ 
City-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
Industry-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
City-industry fixed effects & No & No & No & Yes & Yes & Yes \\ 
Observations & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 \\ 
R$^{2}$ & 0.346 & 0.346 & 0.346 & 0.851 & 0.851 & 0.851 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
Due to limited space, only the coefficients of interest are presented 
for the regressions with city,industry, year fixed effect (i.e. columns 1-3).
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\% \
heteroscedasticity-robust standard errors in parentheses are clustered by city 
}

### 2020-04-27 Temp_tables/Temp_tables_revision/03_Paper_version_Revised/11_decile_8.tex
back up before new paper

\begin{document}% Date and time \times Sat, Apr 04, 2020 - 14:51:25
\begin{table}[!htbp] \centering 
  \caption{Decile 7} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{Dependent variable \times \text { SO2 emission }_{i k t}} \\ 
\cline{2-7} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\
 \\[-1.8ex]& Output & Capital & Labour & Output & Capital & Labour\\
 \hline \\[-1.8ex] 
  output_{cit} & 0.136 & 0.136 & 0.137 & $-$0.059 & $-$0.059 & $-$0.059 \\ 
  & (0.154) & (0.154) & (0.154) & (0.114) & (0.114) & (0.113) \\ 
  capital_{cit} & 1.511$^{**}$ & 1.513$^{**}$ & 1.511$^{**}$ & 0.929$^{*}$ & 0.933$^{**}$ & 0.937$^{**}$ \\ 
  & (0.733) & (0.735) & (0.735) & (0.476) & (0.475) & (0.474) \\ 
  labour_{cit} & 3.038$^{***}$ & 3.041$^{***}$ & 3.035$^{***}$ & 1.550 & 1.545 & 1.538 \\ 
  & (0.829) & (0.831) & (0.829) & (1.023) & (1.023) & (1.021) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 7}_{i} & $-$0.304$^{**}$ & $-$0.305$^{**}$ & $-$0.324$^{**}$ & $-$0.298$^{**}$ & $-$0.336$^{**}$ & $-$0.377$^{**}$ \\ 
  & (0.124) & (0.135) & (0.136) & (0.142) & (0.154) & (0.154) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 7}_{i} \times \text{output share SOE}_{i}  & 1.127$^{**}$ &  &  & 1.315$^{**}$ &  &  \\ 
  & (0.533) &  &  & (0.609) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 7}_{i} \times \text{capital share SOE}_{i}  &  & 0.744$^{*}$ &  &  & 1.065$^{**}$ &  \\ 
  &  & (0.431) &  &  & (0.513) &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 7}_{i} \times \text{labour share SOE}_{i}  &  &  & 0.958$^{*}$ &  &  & 1.532$^{**}$ \\ 
  &  &  & (0.528) &  &  & (0.598) \\ 
 \hline \\[-1.8ex] 
City fixed effects & Yes & Yes & Yes & No & No & No \\ 
Industry fixed effects & Yes & Yes & Yes & No & No & No \\ 
Year fixed effects & Yes & Yes & Yes & No & No & No \\ 
City-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
Industry-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
City-industry fixed effects & No & No & No & Yes & Yes & Yes \\ 
Observations & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 \\ 
R$^{2}$ & 0.346 & 0.346 & 0.346 & 0.851 & 0.851 & 0.851 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
Due to limited space, only the coefficients of interest are presented 
for the regressions with city,industry, year fixed effect (i.e. columns 1-3).
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\% \
heteroscedasticity-robust standard errors in parentheses are clustered by city 
}

>>>>

\begin{document}% Date and time \times Sat, Apr 04, 2020 - 14:52:09
\begin{table}[!htbp] \centering 
  \caption{Decile 8} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{Dependent variable \times \text { SO2 emission }_{i k t}} \\ 
\cline{2-7} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\
 \\[-1.8ex]& Output & Capital & Labour & Output & Capital & Labour\\
 \hline \\[-1.8ex] 
  output_{cit} & 0.136 & 0.137 & 0.137 & $-$0.058 & $-$0.058 & $-$0.059 \\ 
  & (0.154) & (0.154) & (0.154) & (0.114) & (0.114) & (0.114) \\ 
  capital_{cit} & 1.506$^{**}$ & 1.507$^{**}$ & 1.508$^{**}$ & 0.925$^{*}$ & 0.928$^{*}$ & 0.930$^{**}$ \\ 
  & (0.732) & (0.733) & (0.733) & (0.475) & (0.474) & (0.474) \\ 
  labour_{cit} & 3.040$^{***}$ & 3.043$^{***}$ & 3.035$^{***}$ & 1.546 & 1.545 & 1.540 \\ 
  & (0.829) & (0.832) & (0.829) & (1.019) & (1.019) & (1.018) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 8}_{i} & $-$0.306$^{**}$ & $-$0.307$^{**}$ & $-$0.308$^{**}$ & $-$0.303$^{**}$ & $-$0.323$^{**}$ & $-$0.338$^{**}$ \\ 
  & (0.122) & (0.133) & (0.134) & (0.140) & (0.149) & (0.152) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 8}_{i} \times \text{output share SOE}_{i}  & 0.723 &  &  & 1.084$^{*}$ &  &  \\ 
  & (0.548) &  &  & (0.601) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 8}_{i} \times \text{capital share SOE}_{i}  &  & 0.457 &  &  & 0.820 &  \\ 
  &  & (0.448) &  &  & (0.514) &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted decile 8}_{i} \times \text{labour share SOE}_{i}  &  &  & 0.540 &  &  & 1.046$^{*}$ \\ 
  &  &  & (0.523) &  &  & (0.594) \\ 
 \hline \\[-1.8ex] 
City fixed effects & Yes & Yes & Yes & No & No & No \\ 
Industry fixed effects & Yes & Yes & Yes & No & No & No \\ 
Year fixed effects & Yes & Yes & Yes & No & No & No \\ 
City-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
Industry-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
City-industry fixed effects & No & No & No & Yes & Yes & Yes \\ 
Observations & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 \\ 
R$^{2}$ & 0.346 & 0.346 & 0.346 & 0.851 & 0.851 & 0.851 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
Due to limited space, only the coefficients of interest are presented 
for the regressions with city,industry, year fixed effect (i.e. columns 1-3).
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\% \
heteroscedasticity-robust standard errors in parentheses are clustered by city 
}

### 2020-04-27 Temp_tables/Temp_tables_revision/04_city_industry/04bis_table_7_rob_3.tex
back up before new paper

\begin{document}% Date and time \times Sun, Apr 05, 2020 - 10:33:34
\begin{table}[!htbp] \centering 
  \caption{Presence of Foreign firms} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{Dependent variable \times \text { SO2 emission }_{i k t}} \\ 
\cline{2-7} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\
 \\[-1.8ex]& Output & Capital & Labour & Output & Capital & Labour\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.101 & $-$0.101 & $-$0.051 & 0.078 & 0.123 & 0.044 \\ 
  & (0.169) & (0.164) & (0.156) & (0.211) & (0.203) & (0.180) \\ 
   TCZ_c \times \text{Period} \times \text{output share Foreign}_{i} & $-$0.387 &  &  & 0.937 &  &  \\ 
  & (0.662) &  &  & (0.919) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{output share Foreign}_{i} & $-$0.299 &  &  & $-$1.448 &  &  \\ 
  & (1.019) &  &  & (1.237) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{capital share Foreign}_{i}  &  & $-$0.291 &  &  & 0.984 &  \\ 
  &  & (0.620) &  &  & (0.781) &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{capital share Foreign}_{i}  &  & $-$0.249 &  &  & $-$1.710 &  \\ 
  &  & (0.942) &  &  & (1.109) &  \\ 
   TCZ_c \times \text{Period} \times \text{labour share Foreign}_{i}  &  &  & 0.004 &  &  & 1.203 \\ 
  &  &  & (0.599) &  &  & (0.757) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{labour share Foreign}_{i}  &  &  & $-$0.798 &  &  & $-$1.172 \\ 
  &  &  & (1.162) &  &  & (1.167) \\ 
 \hline \\[-1.8ex] 
City fixed effects & Yes & Yes & Yes & No & No & No \\ 
Industry fixed effects & Yes & Yes & Yes & No & No & No \\ 
Yes fixed effects & Yes & Yes & Yes & No & No & No \\ 
City-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
Industry-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
City-industry fixed effects & No & No & No & Yes & Yes & Yes \\ 
Observations & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 \\ 
R$^{2}$ & 0.346 & 0.346 & 0.346 & 0.851 & 0.851 & 0.851 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
Due to limited space, only the coefficients of interest are presented 
for the regressions with city,industry, year fixed effect (i.e. columns 1-3).
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\% \
heteroscedasticity-robust standard errors in parentheses are clustered by city 
}

>>>>

\begin{document}% Date and time \times Sun, Apr 05, 2020 - 10:34:36
\begin{table}[!htbp] \centering 
  \caption{Presence of Foreign firms} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{Dependent variable \times \text { SO2 emission }_{i k t}} \\ 
\cline{2-7} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\
 \\[-1.8ex]& Output & Capital & Labour & Output & Capital & Labour\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.422$^{*}$ & $-$0.521$^{*}$ & $-$0.356 & $-$0.186 & $-$0.274 & $-$0.347 \\ 
  & (0.228) & (0.288) & (0.258) & (0.296) & (0.347) & (0.305) \\ 
   TCZ_c \times \text{Period} \times \text{output share Foreign}_{i} & $-$0.647 &  &  & 0.326 &  &  \\ 
  & (0.756) &  &  & (1.090) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{output share SOE}_{ci} \_ & $-$0.377 &  &  & $-$0.844 &  &  \\ 
  & (0.466) &  &  & (0.597) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{output share Foreign}_{i} & 0.719 &  &  & $-$0.626 &  &  \\ 
  & (1.097) &  &  & (1.406) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{output share SOE}_{ci} \_ & 1.069$^{*}$ &  &  & 1.030 &  &  \\ 
  & (0.568) &  &  & (0.673) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{capital share Foreign}_{i}  &  & $-$0.525 &  &  & 0.109 &  \\ 
  &  & (0.805) &  &  & (0.995) &  \\ 
   TCZ_c \times \text{Period} \times \text{capital share SOE}_{ci} \_ &  & $-$0.209 &  &  & $-$0.751 &  \\ 
  &  & (0.406) &  &  & (0.495) &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{capital share Foreign}_{i}  &  & 1.094 &  &  & $-$0.527 &  \\ 
  &  & (1.156) &  &  & (1.401) &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{capital share SOE}_{ci} \_ &  & 0.827 &  &  & 0.918 &  \\ 
  &  & (0.536) &  &  & (0.606) &  \\ 
   TCZ_c \times \text{Period} \times \text{labour share Foreign}_{i}  &  &  & $-$0.129 &  &  & 0.475 \\ 
  &  &  & (0.737) &  &  & (0.983) \\ 
   TCZ_c \times \text{Period} \times \text{labour share SOE}_{ci} \_ &  &  & $-$0.177 &  &  & $-$0.843 \\ 
  &  &  & (0.455) &  &  & (0.601) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{labour share Foreign}_{i}  &  &  & 0.230 &  &  & 0.014 \\ 
  &  &  & (1.314) &  &  & (1.399) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{labour share SOE}_{ci} \_ &  &  & 0.778 &  &  & 1.154$^{*}$ \\ 
  &  &  & (0.567) &  &  & (0.664) \\ 
 \hline \\[-1.8ex] 
City fixed effects & Yes & Yes & Yes & No & No & No \\ 
Industry fixed effects & Yes & Yes & Yes & No & No & No \\ 
Yes fixed effects & Yes & Yes & Yes & No & No & No \\ 
City-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
Industry-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
City-industry fixed effects & No & No & No & Yes & Yes & Yes \\ 
Observations & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 \\
R$^{2}$ & 0.346 & 0.346 & 0.346 & 0.851 & 0.851 & 0.851 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
Due to limited space, only the coefficients of interest are presented 
for the regressions with city,industry, year fixed effect (i.e. columns 1-3).
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\% \
heteroscedasticity-robust standard errors in parentheses are clustered by city 
}
